---
title: "Australia Weather Analysis from 2008 to 2017"
author: "Abilash Rao Vavilala"
date: "31/07/2021"
output: html_document
---

This Report will provide you easy interpretation of Weather Analysis in Australia from 2008 to 2017. The source of this data is from Australian Government Bureau of Meteorology. The observation of weather in Australia is monitored by Australian Government Bureau of Meteorology. We have Data for 49 cities and regions across Australia. however, we will mainly focus on weather in Two Major cities Sydney and Melbourne. Hottest Day recorded durig this period is 48.1.  this was in woomera on 2011 - 01- 25.



```{r}
library(lubridate)
library(tidyverse)
library(readxl)
library(readr)
urlfile <- "https://raw.githubusercontent.com/AbiVavilala/Australian-Weather-Report/main/weatherAUS.csv"

weather <- read.csv(url(urlfile))
weather$Date <- as.Date(weather$Date)
weather$year <- year(weather$Date)
weather$month <- months(weather$Date)
weather$month <- factor(weather$month, levels = month.name)
 
max(weather$MaxTemp, na.rm = T)
unique(weather$Location)


```

# Temperature analysis for Sydney fromm 2008 to 2017:


We will look at the minimum and maximum temperature recorded in Sydney for this time period. I will provided Graphical representation so we can clearly see there is a clear increase in Temperature

```{r}
sydney_weather <- weather %>% filter(Location == "Sydney")
sydney_weather$temp_interval <- cut(sydney_weather$MaxTemp, breaks = seq(0,50, by = 3))


sydney_weather %>% ggplot(aes(MaxTemp, MinTemp)) + geom_point() + ggtitle("Min and Max temperature recorded in Sydney from 2008 to 2017") + facet_grid(.~year)

```


In the picture above you can clearly see that temperature in Sydney has been incresing every year. In graph, we can see data is moving towards right. This proves temperatures are rising in Sydney. we will Average Temperature in Sydney fromm 2008.

```{r}
syd_2008 <- sydney_weather %>% filter(sydney_weather$year == "2008") 

syd_2009 <- sydney_weather %>% filter(sydney_weather$year == "2009") 

syd_2010 <- sydney_weather %>% filter(sydney_weather$year == "2010") 

syd_2011 <- sydney_weather %>% filter(sydney_weather$year == "2011")


syd_2012 <- sydney_weather %>% filter(sydney_weather$year == "2012")

syd_2013 <- sydney_weather %>% filter(sydney_weather$year == "2013")

syd_2014 <- sydney_weather %>% filter(sydney_weather$year == "2014")

syd_2015 <- sydney_weather %>% filter(sydney_weather$year == "2015")

syd_2016 <- sydney_weather %>% filter(sydney_weather$year == "2016")


syd_2017 <- sydney_weather %>% filter(sydney_weather$year == "2017")





```


According to Climate Change experts before Industrialization average temperature rise recorded was negative. however, after Industrial revolution in 19th century Temperature started increasing on earth surface. 20th century Temperature has risen by 1 degree Celsius. after 1970s average increase in Temperature recorded evry month is 1 degree celsius. Below analysis will prove this claim

```{r}

mean(syd_2008$MaxTemp, na.rm = T)

mean(syd_2009$MaxTemp, na.rm = T)

mean(syd_2010$MaxTemp, na.rm = T)

mean(syd_2011$MaxTemp, na.rm = T)

mean(syd_2012$MaxTemp, na.rm = T)

mean(syd_2013$MaxTemp, na.rm = T)

mean(syd_2014$MaxTemp, na.rm = T)

mean(syd_2015$MaxTemp, na.rm = T)

mean(syd_2016$MaxTemp, na.rm = T)

mean(syd_2017$MaxTemp, na.rm = T)

```


you can clearly see the recorded temperature in Sydney every year has increased. in 2008, average temperature recorded is 21.7277 and this has incresed constantly every year. and increased one degree 2 degree celsius by 2016 and this trend is only incresing every year.



```{r}

sydney_weather_2008_2012 <- sydney_weather %>% filter(year %in% c("2008", "2009", "2010", "2011", "2012"))

sydney_weather_2013_2017 <- sydney_weather %>% filter(year %in% c("2013", "2014", "2015", "2016", "2017"))

sydney_weather_2008_2012 %>% ggplot(aes(temp_interval, fill = temp_interval)) + geom_bar() + ggtitle("temp recorded in Sydney from 2008 to 2012") + geom_text(stat='count', aes(label=..count..), vjust=-1)



sydney_weather_2013_2017 %>% ggplot(aes(temp_interval, fill = temp_interval)) + geom_bar() + ggtitle("temp recorded in sydney from 2013 to 2017") + geom_text(stat='count', aes(label=..count..), vjust=-1)



```



436 days have recorded temperature in between 18-21 in Sydney from 2008 to 2013. 405 days have recorded temperature of 24-27 in 2013 to 2017. days are getting hot. this pattern can be noticed from this data. Days are getting hotter. average temperatures are rising.



# Temperature in Sydney during the day:

we have data for temperature in Sydney at 9AM and 3PM. lets see if temperature are rising during the day. 

```{r}
sydney_weather %>% ggplot(aes(Temp9am, Temp3pm)) + geom_point() + facet_grid(.~year)
```


data shows us that Temperature has been on rise every year. Days are getting hotter every year


# Rainfall in Sydney from 2008 to 2017:

In the dataset we also have data for rainfall in Sydney from 2008 to 2017. we will analyse the data and see if there is any pattern for rainfall.



 